Sound Automated Synthesis of Digital Controllers

### 2016-10-12 paper/paper.tex
chenged the CEGIS figure to support the two verifiers

For this purpose, the design procedure is based on a discretized model for a continuous plant. Considering only transfer function models, we are interested in a $z$-domain transfer function that considers all the aspects about the continuous plant ($G(s)$) and the sampling and hold process.

Note that $G(z)$ is a discrete model of a real (and continuous) plant, {\it
i.e.}, a continuous model of the plant must be discretized to obtain the
discrete equivalent coefficients via ZOH
discretization.

%\red{[why do we discuss the ZOH at this point?]}

@@

Uncertainties in $G(z)$ may appear due to uncertainties in $G(s)$ (\emph{i.e.} $\Delta{G}_p(s)$), errors in the numeric calculations, or roundoffs in the quantization.
These uncertainties may be parametrically expressed by an additive transfer function $\Delta G(z)$, resulting in a uncertain model $\hat{G}(z)$, such that:
\begin{equation}
\hat{G}(z)=G(z)+\Delta G(z),
\end{equation}
which will be represented by the following transfer function:
\begin{equation}
\hat{G}(z)=\frac{\hat{b}_{0}+\hat{b}_{1}z^{-1}+...+\hat{b}_{M_G}z^{-M_G}}{\hat{a}_{0}+\hat{a}_{1}z^{-1}+...+\hat{a}_{N_G}z^{-N_G}} : N_G \geq M_G .
\end{equation}
\red{[same order?]}

@@

%
In figure~\ref{fig:digsystem1}, two sources of uncertainties are considered: parametric uncertainties related to modeling errors, and uncertainties introduced by quantisations in sampling and holding process, {\it i.e.} ADC and DAC conversions. Assuming linearity and independence between these sources, the uncertain model may be rewritten as follows:
\begin{equation}
\label{eq:complete_unc_model}
\hat{G}(z)=G(z)+\Delta G_{P}(z)+\Delta G_{Q}(z),
\end{equation}
where $\Delta G_{P}(z)$ is the term that corresponds to the parametric uncertainties and $\Delta G_{Q}(z)$ is the term that reflects the quantisation effects on the plant model. %\red{[next figure is a bit unnecessary, does not ad much to the previous one.]} Figure~\ref{fig:digsystem2} shows the digital closed loop systems with $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$.

%\begin{figure}[ht]
%\centering
%
%\tikzset{add/.style n args={4}{
%    minimum width=6mm,
%    path picture={
%        \draw[circle] 
%            (path picture bounding box.south east) -- (path picture bounding box.north west)
%            (path picture bounding box.south west) -- (path picture bounding box.north east);
%        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
%        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
%        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
%        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
%        }
%    }
% }
%
%\resizebox{.5\textwidth}{!}{
% \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
%     semithick, initial text=, ampersand replacement=\&,]
%
%  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
%  %
%	\& 
%	\&
%	\& \coordinate (aux7); 
%	\& \node[rectangle,draw,
%	minimum width=1cm,
%	minimum height=1cm] (deltag2) {{\sc $\Delta G_{Q}(z)$}};
%	\& \coordinate (aux8);\\
%    \node[draw=none] (r) {$R(z)$};
%%   \& \coordinate (aux0);
%   \& \node[circle,add={-}{+}{}{}] (circle) {};
%   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
%   \& \node[rectangle,draw,
%	minimum width=1cm,
%	minimum height=1cm,
%        label=\textbf{Controller}] (cz) {{\sc C(z)}};
%   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
%   \& \coordinate (aux4);
%   \& \node[rectangle,draw,
%	minimum width=1cm,
%	minimum height=1cm,
%        label=\textbf{Plant}] (gs) {{\sc G(z)}};
%   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(z)$};
%   \& \node[circle,add={+}{+}{+}{}] (circle2) {};
%%   \node[draw=none] (tyz) at ([xshift=-1cm,yshift=.15cm]circle2)  {$Y(z)$};
%%   \node[draw=none] (nu) at ([yshift=1cm]circle2)  {$\nu(z)$};
%   \& \coordinate (aux1);
%   \& \node[draw=none] (yz) {$\hat{Y}(z)$};\\
%   \& 
%   \&
%   \& \coordinate (aux5); 
%   \& \node[rectangle,draw,
%	minimum width=1cm,
%	minimum height=1cm] (deltag) {{\sc $\Delta G_{P}(z)$}};
%   \& \coordinate (aux6);\\
%   \& \coordinate (aux3); 
%   \&
%   \& 
%   \& 
%   \&
%   \& \coordinate (aux2);\\
%  };
%
%
%%  \path[->] (v1) edge (q1.north);
%%  \path[->] (v2) edge (q2.north);
%  \path[->] (r) edge (circle.west);
%%  \path[->] (nu) edge (circle2.north);
%  \path[->] (aux1) edge (yz);
%  \path  
%   (aux4.north) edge (aux5.south)
%   (aux4.north) edge (aux7.south)
%   (aux5.east) edge (deltag.west)
%   (aux7.east) edge (deltag2.west)
%   (deltag.east) edge (aux6.west)
%   (deltag2.east) edge (aux8.west)
%   (circle.east) edge (cz)
%   (cz.east) edge (gs.west)
%   (circle2.east) edge (aux1.west)
%   (aux1.south) edge (aux2.north)
%   (aux2.west) edge (aux3.east); 
%  \path[->] (aux8.south) edge (circle2.north); 
%  \path[->] (aux6.south) edge (circle2.south);
%  \path[->] (gs.east) edge (circle2.west);
%  \path[->] (aux3.north) edge (circle.south);
% \end{tikzpicture}
%}
% \caption{Digital system with additive uncertainties $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$. \label{fig:digsystem2}}
%\end{figure}

@@

\begin{figure*}
\centering
\resizebox{.7\textwidth}{!}{
 \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=1cm, column sep=1cm] {
   \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}}; \\
   \node[fill=yellow!20] (synth) {{\sc Synthesise}};
   \&
   \node[fill=yellow!20] (verif) {{\sc Verify}}; \\

   \& \\
   \& \\
   \node (gp) {~~~~~~~~~~~~~~Closed-loop System Search~~~~~~~~~~~~~~~};
   \&
   \node (bmc) {~~~~~~~~~~~~~~~BMC-based Verifier~~~~~~~~~~~~~~~};

    \\
  };

   \path
    ([yshift=2em]synth.east) edge node {Candidate solution} ([yshift=2em]verif.west)
    ([yshift=-2em]verif.west) edge node {Counterexample} ([yshift=-2em]synth.east)
    ([xshift=5em]verif.south) edge node {Candidate $P$} ([xshift=5em]bmc.north)
    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif.south)
    (verif) edge node {} (done)
    ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\candidate} ([xshift=-5em]synth.south);
 \end{tikzpicture}
}
 \caption{Counterexample-Guided Inductive Synthesis of Closed-loop System (CEGIS paradigm). \label{fig:CEGIS}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experimental Evaluation}

>>>>

For this purpose, the design procedure is based on a discretized model for a continuous plant. For transfer function models, we are interested in a $z$-domain transfer function that considers all the aspects about the continuous plant ($G(s)$) and the sampling and hold process.

Note that $G(z)$ is a discrete model of a real (and continuous) plant, {\it
i.e.}, a continuous model of the plant must be discretized to obtain the
discrete equivalent coefficients $b$ and $a$~\cite{Astrom08} via ZOH
discretization.

\red{[why do we discuss the ZOH at this point?]}

@@

Uncertainties in $G(z)$ may appear due to uncertainties in $G(s)$ (\emph{ie} $\Delta{G}_p(s)$), errors in the numeric calculations, or roundoffs in the quantization.
These uncertainties may be parametrically expressed by an additive transfer function $\Delta G(z)$, resulting in a uncertain model $\hat{G}(z)$, such that:
\begin{equation}
\hat{G}(z)=G(z)+\Delta G(z),
\end{equation}
which will be represented by the following transfer function:
\begin{equation}
\hat{G}(z)=\frac{\hat{b}_{0}+\hat{b}_{1}z^{-1}+...+\hat{b}_{M_G}z^{-M_G}}{\hat{a}_{0}+\hat{a}_{1}z^{-1}+...+\hat{a}_{N_G}z^{-N_G}} : N_G \geq M_G .
\end{equation}
\red{[same order?]}

@@

%
In figure~\ref{fig:digsystem1}, two sources of uncertainties are considered: parametric uncertainties related to modeling errors, and uncertainties introduced by quantisations in sampling and holding process, {\it i.e.} ADC and DAC conversions. Assuming linearity and independence between these sources, the uncertain model may be rewritten as follows:
\begin{equation}
\label{eq:complete_unc_model}
\hat{G}(z)=G(z)+\Delta G_{P}(z)+\Delta G_{Q}(z),
\end{equation}
where $\Delta G_{P}(z)$ is the term that corresponds to the parametric uncertainties and $\Delta G_{Q}(z)$ is the term that reflects the quantisation effects on the plant model. \red{[next figure is a bit unnecessary, does not ad much to the previous one.]} Figure~\ref{fig:digsystem2} shows the digital closed loop systems with $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$.

  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
  %
	\& 
	\&
	\& \coordinate (aux7); 
	\& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm] (deltag2) {{\sc $\Delta G_{Q}(z)$}};
	\& \coordinate (aux8);\\
    \node[draw=none] (r) {$R(z)$};
%   \& \coordinate (aux0);
   \& \node[circle,add={-}{+}{}{}] (circle) {};
   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Controller}] (cz) {{\sc C(z)}};
   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
   \& \coordinate (aux4);
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Plant}] (gs) {{\sc G(z)}};
   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(z)$};
   \& \node[circle,add={+}{+}{+}{}] (circle2) {};
%   \node[draw=none] (tyz) at ([xshift=-1cm,yshift=.15cm]circle2)  {$Y(z)$};
%   \node[draw=none] (nu) at ([yshift=1cm]circle2)  {$\nu(z)$};
   \& \coordinate (aux1);
   \& \node[draw=none] (yz) {$\hat{Y}(z)$};\\
   \& 
   \&
   \& \coordinate (aux5); 
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm] (deltag) {{\sc $\Delta G_{P}(z)$}};
   \& \coordinate (aux6);\\
   \& \coordinate (aux3); 
   \&
   \& 
   \& 
   \&
   \& \coordinate (aux2);\\
  };

%  \path[->] (v1) edge (q1.north);
%  \path[->] (v2) edge (q2.north);
  \path[->] (r) edge (circle.west);
%  \path[->] (nu) edge (circle2.north);
  \path[->] (aux1) edge (yz);
  \path  
   (aux4.north) edge (aux5.south)
   (aux4.north) edge (aux7.south)
   (aux5.east) edge (deltag.west)
   (aux7.east) edge (deltag2.west)
   (deltag.east) edge (aux6.west)
   (deltag2.east) edge (aux8.west)
   (circle.east) edge (cz)
   (cz.east) edge (gs.west)
   (circle2.east) edge (aux1.west)
   (aux1.south) edge (aux2.north)
   (aux2.west) edge (aux3.east); 
  \path[->] (aux8.south) edge (circle2.north); 
  \path[->] (aux6.south) edge (circle2.south);
  \path[->] (gs.east) edge (circle2.west);
  \path[->] (aux3.north) edge (circle.south);
 \end{tikzpicture}
}
 \caption{Digital system with additive uncertainties $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$. \label{fig:digsystem2}}
\end{figure}

@@

\begin{figure*}
\centering
\resizebox{.7\textwidth}{!}{
 \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=1cm, column sep=1.5cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \&;\\
   \node[fill=yellow!20] (synth) {{\sc Synthesise}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dashed,
	minimum width=7cm,
	minimum height=1.6cm,
	label={\sc Verify},] (verif) {};
   \node[fill=yellow!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc Uncertainty}};
   \node[fill=yellow!20] (verif2) at ([xshift=2cm]verif.center) {{\sc Precision}};
   } 
   \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}};\\
   %% \node[fill=yellow!20] (verif) {{\sc ~~~~~~Uncertainty~~~~~~}};
   %% \&
   %% \node[fill=yellow!20] (verif2) {{\sc ~~~~~~Precision~~~~~~~}};\\
   \& \\
   \& \\
   \node (gp) {Closed-loop System Search};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node (bmc) at ([xshift=-2cm]aux.center) {BMC-based Verifier};
   \node (fp)  at ([xshift=2cm]aux.center) {Fixed-point \\Arithmetic Verifier};
   }   
    \\
  };

   \path
    ([yshift=2em]synth.east) edge node {Candidate solution} ([yshift=2em]verif1.west)
    ([yshift=-2em]verif1.west) edge node {Counterexample} ([yshift=-2em]synth.east)
    ([xshift=5em]verif1.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]bmc.north)
    ([xshift=5em]verif2.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]fp.north)
    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south)
    ([xshift=-5em]fp.north) edge node[align=center]  {True/\\False} ([xshift=-5em]verif2.south)
    (verif2) edge node {} (done)
    ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\candidate} ([xshift=-5em]synth.south)
    (aux1) edge (synth.north);
   \path[-]
   (verif2.north) edge node[align=center] {} ([xshift=6.7cm]aux2)
   ([xshift=6.7cm]aux2) edge node[align=center] {Reset} (aux1);

 \end{tikzpicture}
}
 \caption{Counterexample-Guided Inductive Synthesis of Closed-loop System (CEGIS paradigm). \label{fig:CEGIS}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experimental Evaluation}
